Feasibility Study for the Final State $hh\rightarrow (b\bar{b})(b\bar{b})$

### 2015-01-20 doc/HH4b_Documentation.tex
small updates

\subsubsection{Resolved $b$-jet tagging efficiencies}
In order to perform an initial validation of the b-tagging procedure used in our resolved analysis we consider first a simple flat b-jet tagging efficiency of $\epsilon_b=0.8$ and a light jet mis-tag rate of $\epsilon_l=0.01$. In the UCL diHiggs analysis~\cite{Wardrope:2014kya} the 2$b$2$j$ background was discarded by applying a naive selection factor of $\epsilon^2_l\epsilon^2_b$ to a similar $2b2j$ cross-section as in Table~\ref{tab:xsecs} and finding the resulting cross-section to be considerably smaller than the equivalent selection factor applied to the 4$b$ sample.

In practice we have found with these simple efficiencies, that the actual selection efficiencies differ considerably from the naive factors of $\epsilon_b^{n_b}\epsilon_l^{n_l}$.
In Table~\ref{tab:btageff1} the results of this simple b-tagging test are demonstrated. Shown in the table are the total cross-sections before and after the application of the described b-tagging procedure, the resulting percentage of the cross-section passing the b-tag, and the naive selection percentage that would result from applying powers of $\epsilon_{b/l}$ to the total cross-section. The pass rate for samples with four $b$ quarks in the final state is therefore considerably lower in practice than one would naively expect, and the pass rate for the $2b2j$ sample considerably higher.

@@

\subsubsection{$b$-jet tagging efficiencies with UCL-style selection}
In the UCL analysis their jet selection does not proceed as described in the previous section, presumably as requiring the four hardest jets in the event to be b-Tagged cuts too aggressively upon the signal process. Rather, the selection proceeds by taking all anti-$k_T$ $R=0.5$ jets with $p_T > 40$ GeV and running the b-Tagging algorithm on them. The four hardest successfully b-tagged jets are then selected for further analysis. With such a method implemented for our samples and with our previous selection efficiencies and fake rates, Table \ref{tab:UCLbtag} summarises the results.

>>>>

\subsubsection{Resolved $b$-jet tagging efficiencies}
In order to perform an initial validation of the $b$-tagging procedure used in our resolved analysis we consider first a simple flat $b$-jet tagging efficiency of $\epsilon_b=0.8$ and a light jet mis-tag rate of $\epsilon_l=0.01$. In the UCL diHiggs analysis~\cite{Wardrope:2014kya} the 2$b$2$j$ background was discarded by applying a naive selection factor of $\epsilon^2_l\epsilon^2_b$ to a similar $2b2j$ cross-section as in Table~\ref{tab:xsecs} and finding the resulting cross-section to be considerably smaller than the equivalent selection factor applied to the 4$b$ sample.

In practice we have found with these simple efficiencies, that the actual selection efficiencies differ considerably from the naive factors of $\epsilon_b^{n_b}\epsilon_l^{n_l}$.
In Table~\ref{tab:btageff1} the results of this simple $b$-tagging test are demonstrated. Shown in the table are the total cross-sections before and after the application of the described $b$-tagging procedure, the resulting percentage of the cross-section passing the b-tag, and the naive selection percentage that would result from applying powers of $\epsilon_{b/l}$ to the total cross-section. The pass rate for samples with four $b$ quarks in the final state is therefore considerably lower in practice than one would naively expect, and the pass rate for the $2b2j$ sample considerably higher.

@@

\subsubsection{$b$-jet tagging efficiencies with UCL-style selection}
In the UCL analysis their jet selection does not proceed as described in the previous section, presumably as requiring the four hardest jets in the event to be $b$-tagged cut too aggressively into the signal process. Rather, the selection proceeds by taking all anti-$k_T$ $R=0.5$ jets with $p_T > 40$ GeV and running the $b$-tagging algorithm on them. The four hardest successfully $b$-tagged jets are then selected for further analysis. With such a method implemented for our samples and with our previous selection efficiencies and fake rates, Table \ref{tab:UCLbtag} summarises the results.
